\subsection{Achievements and Prizes}

Note: "Kill a Character" means causing a Character death by:
\begin{itemize}
	\item Killing it directly.
	\item Having it killed by a Mine (Active) Room set by yourself.
	\item Pushing it in a Death Room.
	\item Having it killed by a Rolling Rock triggered by yourself.
	\item Having a Drone kill it after designating that Character as Target for that Drone.
\end{itemize}

The game will have Achievements and Prizes. Both grant a Steam Achievement to the player's Steam account the first time they're earned.
Achievements can only be earned once and will grant a large amount of in-game currency once earned. Prizes can be earned multiple times, and each time grant a small amount of in-game currency.

\subsubsection{Achievements}

\paragraph{White Death} Kill a total of 259 Characters.
\paragraph{Säkkijärven Polka} Turn a total of 1941 Mine (Active) Rooms into Mine (Inactive) Rooms.
\paragraph{Mercator} Reveal the entirety of the Rooms a total of 1512 times.

\paragraph{Good old Games} Win the Gaming Room a total of 2008 times.
\paragraph{Rutabaga} Have your Character survive a Rolling Rock a total of 7 times
\paragraph{Woah!} Have your Character Killed by a Rolling Rock triggered from yourself a total of 7 times.

\subsubsection{Prizes}

\paragraph{Reaper} Kill all the other Characters in a Free For All Match.
\paragraph{Slaughter} Win a Team Match by having the entirety of the enemy Team Killed.
\paragraph{United} Win a Team Match with no losses in your Team.
\paragraph{Sly} Win a match being the last Character alive.
\paragraph{Cartographer} Reveal the entirety of the Rooms.
\paragraph{Backstab} Kill a Character who has previously Healed your Character.

\paragraph{Terminator} Kill a Character targeting him with a Drone.
\paragraph{Collateral} Have your Character Killed by a Drone connected to a Drone Room after you failed its minigame.


\pagebreak 